Refunctionalization of Abstracting Abstract Machines (Functional Pearl)

### 2018-03-17 paper.tex
2.3.3

  \item An atomic expression @ae@ sits on the control position of the state.
The value of @ae@ is being returned to its caller.
We dereference the continuation address @kaddr@ and obtain a set of
continuations @conts@.
For each continuation in the set, we construct an environment based on the
environment of the frame (@env_f@), and bind @x@ to a newly created binding
address @baddr@; also update the store with @baddr@ and
the values that @ae@ represents. In every generated states,
the control becomes the expression @e@ in the frame,
and as we can tell from the name, continuation address @f_kaddr@
also comes from the frame.
\end{itemize}

>>>>

  \item In the second case, an atomic expression @ae@ sits on the control position of the
state. Here, the value of @ae@ is being returned to its caller.
In order to accomplish this, we dereference the continuation address @kaddr@ and obtain a set
of continuations @conts@. For each continuation in the set, we construct an environment based
on the environment @env_f@ of the frame, and bind @x@ to a newly created binding address
@baddr@. We must also update the store with @baddr@ and the values that @ae@ represents. In
every generated state, the control becomes the expression @e@ in the frame, and as we can
tell from the name, the continuation address @f_kaddr@ also comes from the frame.
\end{itemize}
